\cvsection{Projects}
\cvproject{\href{}{Data Platform} (DevOps)}
\begin{itemize}
\item International Humanitarian Organization Project.
\smallskip

Designed and developed a fully automated ETL (Extract, Transform, Load) solution to increase data processing efficiency while reducing data analyst workload. Implemented a Single Point of Truth (SPOT) architecture to ensure the consolidation of a unified and secure data source in a sensitive international context.
\end{itemize}
\smallskip
\smallskip

\cvsection{SKILLS}
\cvproject{Scripting and Programming Languages}
\begin{itemize}
 \item \cvskill{Python}{3}
 \item \cvskill{Bash}{2}
 \item \cvskill{Typescript}{2}
\end{itemize}
\smallskip
\begin{description}
 \item \textbf{OS}: GNU/Linux (Debian and RHEL based), Windows Server.
 \item \textbf{Cloud}: Amazon Web Services(AWS), Azure(Microsoft), Oracle Cloud(OCI).
 \item \textbf{Infrastructure as code(IaC)}: CloudFormation(YAML), CDK(TypeScript, Pyhton), Terraform, Ansible.
 \item \textbf{DevOps}: GIT, Docker, CI/CD Pipelines(AzureDevOps, AWS Code Suite), Github Actions, Jenkins.
 \item \textbf{Data}: AWS Glue, Amazon Redshift, SQL, Tableau.
 \item \textbf{Culture and Process}: Agile, Value Stream Mapping.
\end{description}

\cvsection{Interests}
\cvproject{Technical}
\begin{itemize}
\item Open Source Community
\item ETL/Data oriented projects
\end{itemize}
\smallskip
\cvproject{Hobbies}
\begin{itemize}
\item Self-hosting
\item Cooking (Chef in a not-so-distant past life)
\end{itemize}


\cvsection{Languages}
\begin{itemize}
 \item \cvskill {Italian}{5}
 \item \cvskill {English}{3}
 \item \cvskill {Spanish}{3}
\end{itemize}

